---
title: "An Analysis on Cryptocurrency"
authors: "..., ..."
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
```
## Cryptocurrency Project Overview
Our group hopes to explore the domain of cryptocurrency/blockchain. Cryptocurrency is a form of payment that can be exchanged online for goods and services. Cryptocurrencies work using a technology called blockchain. Blockchain is a decentralized technology spread across many computers that manages and records transactions. Cryptocurrencies are generally not issued by any central authority, rendering them almost immune to government interference or manipulation, an appealing aspect of this technology as trust in banks decline.

We aim to answer several questions with our dataset but our **main goal** is to see *what information can the growth of prices in cryptocurrency tell us.*

### Information on Data Set:

**Cryptocurrency Historical Prices:**

[Link to data set](https://www.kaggle.com/sudalairajkumar/cryptocurrencypricehistory)

This data is taken from [CoinMarketCap](https://coinmarketcap.com/), and it contains the historical prices for different crypto currencies (including daily highs and lows) in dollars. Since it was collected from coinmarketcap, the way that they generated the data is similar to what is described for the dataset above. The exchanges determine prices based on the trading volume of the asset and it’s supply and demand.



## Summary of Data

In order to see the variability of market prices of different cryptocurrencies throughout 2020 which showcased some of the extremes in prices. 
```{r echo=FALSE}
get_summary_kable(all_coins)
```

Something we can take away from this is the extreme varibalilty of prices of crytptocurrency for ethereum there was a drastic difference between the highest price and the lowest price spanning over 700 dollars. We can also see that companies like Dogecoin had extremly low prices with its highest price being .01 cents.

## Price and Market Cap Over Time (Interactive)
```{r echo=FALSE}
marketcap_over_time(all_coins)
price_over_time(all_coins)
```

## Max Market Cap + Volume By Coin
```{r echo=FALSE}
mkt_bar_graph(all_coins)
vol_bar_graph(all_coins)
```

## Candlestick Charts of Bitcoin and Ethereum

Candlestick charts are the most widely accepted and effective ways to represent changes in market activity over time for a given asset, in which case we will be looking at Bitcoin and Ethereum. Each data point, or "candle" in the chart contains information on various price points per day, including the high, low, open, and close prices. A candle with a green body indicates that the price has gone up within that given day, while a red body means the price has gone down.

Below each candlestick chart is an associated volume bar chart, which measures how much of a given coin is traded within each day in USD. From the volume, we can infer which direction the coin is moving next, and is commonly used in tandem with the candlestick chart to understand and predict market trends.

```{r echo=FALSE}
draw_plot(bitcoin, "Bitcoin (BTC)")
```

From the Bitcoin chart, we can see that prior to 2021, the coin has seen peaks (and subsequent drops) at the start of 2018 and mid-2019, before leveling out throughout 2020. In spite of the apparent plateau, after overcoming the steep drop in early 2020, the trading volume began steadily increasing until the end of 2020. This unsurprisingly correlates with the onset of the coronavirus pandemic, and by the start of 2021, massive uptrends grew exponentially as the price of Bitcoin surged dramatically. Just as the coin reached its new high by a wide margin, the price dropped nearly instantly as traders rushed to sell their coins around the peak.

```{r}
draw_plot(ethereum, "Ethereum (ETH)")
```

From the Ethereum chart, we can see a fairly similar pattern to that of Bitcoin, with a substantial peak in 2018 followed by a long plateau from 2019 to late 2020. While the price per coin is much lower than Bitcoin, we can see a much clearer indication in 2021 that trading activity and public interest in the coin were reinforcing the unprecedented bull rush in early 2021. Since then, the price has also taken a significant dip, and may continue correcting itself until a new low is reached.
