---
title: "An Analysis on Cryptocurrency"
authors: "..., ..."
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
```

## Cryptocurrency Project Overview
Our group hopes to explore the domain of cryptocurrency/blockchain. Cryptocurrency is a form of payment that can be exchanged online for goods and services. Cryptocurrencies work using a technology called blockchain. Blockchain is a decentralized technology spread across many computers that manages and records transactions. Cryptocurrencies are generally not issued by any central authority, rendering them almost immune to government interference or manipulation, an appealing aspect of this technology as trust in banks decline.

We aim to answer several questions with our dataset but our **main goal** is to see *what information can the growth of prices in cryptocurrency tell us.*

### Information on Data Set:

**Cryptocurrency Historical Prices:**

[Link to data set](https://www.kaggle.com/sudalairajkumar/cryptocurrencypricehistory)

This data is taken from [CoinMarketCap](https://coinmarketcap.com/), and it contains the historical prices for different crypto currencies (including daily highs and lows) in dollars. Since it was collected from coinmarketcap, the way that they generated the data is similar to what is described for the dataset above. The exchanges determine prices based on the trading volume of the asset and it’s supply and demand.

## Summary of Data

In order to see the variability of market prices of different cryptocurrencies throughout 2020 which showcased some of the extremes in prices. 
```{r echo=FALSE, message=FALSE, warning=FALSE}
get_summary_kable(all_coins)
```

Something we can take away from this is the extreme varibalilty of prices of crytptocurrency for ethereum there was a drastic difference between the highest price and the lowest price spanning over 700 dollars. We can also see that companies like Dogecoin had extremly low prices with its highest price being .01 cents.

## Price and Market Cap Over Time (Interactive)
```{r echo=FALSE, message=FALSE, warning=FALSE}
price_over_time(all_coins)
marketcap_over_time(all_coins)
```

The original data set had a lot of points, which made the rendering of the graph quite laggy. The solution to this was to group the data points by month, which is what the graphs show above. So these charts above represent the price and market cap of a multitude of coins over time grouped by a monthly basis. It represents the relationship between cryptocurrency and the US Dollar over the years and helps give insight to how people value the services the coins give.

The reason we chose to have a scatter plot was because for this information, the clarity of a position based encoding helps a user see clear trends over time and clearly compare/contrast different prices and marketcaps of the various coins.

When looking at the information rendered out, we found that cryptocurrencies have, overall, been on a upward trend. However, even if overall crypto has been going up, we can clearly see two large peaks in price and marketcap within the charts. This revealed the volatility of crypto but also when crypto was popular among investors. However, these peaks were accompanied by huge drops of price, indicating some type of "hype cycle" or catastrophic event that caused the prices to plummet. Another interesting observation we had was how the marketcap trend of Bitcoin is mirrored closely by almost every other coin. While there are some differences, when looking from afar, the shapes that the marketcap plots are very similar.

## Max Market Cap + Volume By Coin
```{r echo=FALSE, message=FALSE, warning=FALSE}
max_mkt
max_vol
```

## Chart 3
```{r echo=FALSE, message=FALSE, warning=FALSE}
draw_plot(bitcoin, "Bitcoin (BTC)")
draw_plot(ethereum, "Ethereum (ETH)")
```
