---
title: "An Analysis on Cryptocurrency"
authors: "..., ..."
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
source("analysis.R")
```
## Cryptocurrency Project Overview
Our group hopes to explore the domain of cryptocurrency/blockchain. Cryptocurrency is a form of payment that can be exchanged online for goods and services. Cryptocurrencies work using a technology called blockchain. Blockchain is a decentralized technology spread across many computers that manages and records transactions. Cryptocurrencies are generally not issued by any central authority, rendering them almost immune to government interference or manipulation, an appealing aspect of this technology as trust in banks decline.

We aim to answer several questions with our dataset but our **main goal** is to see *what information can the growth of prices in cryptocurrency tell us.*

### Information on Data Set:

**Cryptocurrency Historical Prices:**

[Link to data set](https://www.kaggle.com/sudalairajkumar/cryptocurrencypricehistory)

This data is taken from [CoinMarketCap](https://coinmarketcap.com/), and it contains the historical prices for different crypto currencies (including daily highs and lows) in dollars. Since it was collected from coinmarketcap, the way that they generated the data is similar to what is described for the dataset above. The exchanges determine prices based on the trading volume of the asset and it’s supply and demand.



## Summary of Data

In order to see the variability of market prices of different cryptocurrencies throughout 2020 which showcased some of the extremes in prices. 
```{r echo=FALSE}
get_summary_kable(all_coins)
```

Something we can take away from this is the extreme varibalilty of prices of crytptocurrency for ethereum there was a drastic difference between the highest price and the lowest price spanning over 700 dollars. We can also see that companies like Dogecoin had extremly low prices with its highest price being .01 cents.

## Price and Market Cap Over Time (Interactive)
```{r echo=FALSE}
marketcap_over_time(all_coins)
price_over_time(all_coins)
```

## Max Market Cap + Volume By Coin
```{r echo=FALSE}
mkt_bar_graph(all_coins)
vol_bar_graph(all_coins)
```

One of the questions we would like to answer is which crypto-currency has the most
potential to be useful. How do we define usefulness? While there are many definitions
we can use, we settled on a simple one, which is applicable to defining the usefulness
of the dollar as well; namely the ability to conduct transactions. 

One proxy we use to measure ability to conduct transactions is daily volume (total amount of coins switching hands) which in this case is conveniently a dollar amount for cross-coin comparison. One caveat to note with crypto is unlike fiat currency it also functions as a 
speculative asset like a stock, meaning daily volume could be generated by day
traders and other financial services rather than people using it to buy goods and
services. This is in contrast to fiat currencies where most of the volume is 
used for goods and services, and stocks where most of the volume is from day-trading
and other financial programs. Cryptocurrency volume can include both, and while
in terms of determining usefulness, looking at the subset of transactions on
goods and services could have been a better measure, but that would have been
harder to collect. In addition, use in day-trading and other profitable ventures
would make cryptocurrencies useful as those profits could also be used for goods
and services.

I chose the maximum of daily volumes, because seeing how a coin performing at its
best, can be a good indication of its potential. Although determining potential is
in practice much more complicated than this and involves looking at historical trends
and theories of why the coin will continue to improve, the max daily volume is a 
simple enough proxy to visualize.

For this reason I included a visualization for max volume per coin, and I chose
a bar graph because that's visually intuitive to determine the coin with the
highest max volume. Distinguishing coins by colors was primarily done because
the x-axis labels were getting squashed together and it would've been messy to
read.

Another question we would like to answer is which crypto-currency has the potential to be most valuable. In this case, the economic definition of value (market cap) can suffice, as 
crypto currencies are primarily economic assets. 

Again, I chose the maximum market capitalization, because I believe that it is 
a good indication of potential market capitalization. However, I do recognize that
there are more sophisticated proxies for this potential, but I think this proxy
is good enough for our purposes.


## Chart 3
```{r echo=FALSE}
draw_plot(bitcoin, "Bitcoin (BTC)")
draw_plot(ethereum, "Ethereum (ETH)")
```