---
title: "An Analysis on Cryptocurrency"
authors: "..., ..."
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
library(knitr)
library(kableExtra)
source("analysis.R")
```
## Cryptocurrency Project Overview
Our group hopes to explore the domain of cryptocurrency/blockchain. Cryptocurrency is a form of payment that can be exchanged online for goods and services. Cryptocurrencies work using a technology called blockchain. Blockchain is a decentralized technology spread across many computers that manages and records transactions.

We aim to answer several questions with our dataset but our main goal is to see what information can the growth of prices in cryptocurrency tell us.

To achive this we will attempt to answer these following questions:

- How has the usage between the two biggest cryptocurrencies (Bitcoin and Ethereum) compared to each other? Is one growing faster than the other Metrics: Market-cap? Or are they growing equally?
- Which cryptocurrency is the most important in day to day use? 
- What areas of the world are most involved in the cryptocurrency mining process? How much electricity have they used overtime and how has that impacted certain geological areas?
- How does price and price growth impact other parts of a cryptocurrency like mining and geological node locations?

## Summary of Data

In order to see the variability of market prices of different cryptocurrencies throughout 2020 which showcased some of the extremes in prices. 
```{r echo=FALSE}
knitr::kable(summary_table, col.names = c("Name", "Average Change in Daily Price ($)", "Highest Price ($)", "Lowest Price ($)", "Change in Market Cap ($)", "Average Volume (Daily Transacted Amount in $)"), caption = "Cryptocurrency in 2020", "simple")
```
Something we can take away from this is the extreme varibalilty of prices of crytptocurrency for ethereum there was a drastic difference between the highest price and the lowest price spanning over 700 dollars. We can also see that companies like Dogecoin had extremly low prices with its highest price being .01 cents.

## Price and Market Cap Over Time (Interactive)
```{r echo=FALSE}
marketcap_over_time
price_over_time
```

## Chart 2

## Chart 3